---
title: "Evolution of Covid-19 infected cases in France"
author: "Li"
date: "4/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description
This page presents the evolution of Covid-19 infected cases in France. The data from 27/02/2020 are plotted, including the new confirmed infected cases and deaths each day as well as the total cases.  Data are extracted from the site [Open Data of European Centre for Disease Prevention and Control](https://opendata.ecdc.europa.eu/covid19/casedistribution/csv).

```{r, echo=FALSE, message=FALSE}
library(dplyr)
library(plotly)

tf<-tempfile()
download.file("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv",tf)
data <- read.csv(tf)
unlink(tf)



columns <- c('dateRep','countriesAndTerritories', 'cases', 'deaths')

data <- data[columns]
data$dateRep<-as.Date(data$dateRep, format = "%d/%m/%Y")
data_fr<-data%>%
        filter(countriesAndTerritories=='France')%>%
        filter(dateRep>=as.Date('27/02/2020',format="%d/%m/%Y"))
data_fr$cum_cases <-rev(cumsum(rev(data_fr$cases )))
data_fr$cum_deaths <-rev(cumsum(rev(data_fr$deaths )))
```
## Including Plots
Total confirmed cases and deaths:
```{r, echo=FALSE}
fig0 <-plot_ly(x=data_fr$dateRep,y=data_fr$cum_cases,type = 'scatter', mode = 'lines',name = "Total confirmed cases",width = 800, height = 500 )%>%
  add_trace(x=data_fr$dateRep,y=data_fr$cum_deaths,type = 'scatter', mode = 'lines',name = "Total deaths")%>%
  layout(title ="Total confirmed cases and deaths in France from 27/02/2020")
fig0
```


Daily confirmed cases and deaths:
```{r, echo=FALSE}
fig2 <- plot_ly( x=data_fr$dateRep,y=data_fr$cases, type = 'bar', name = 'New confirmed cases',width = 800, height = 500) %>%
        add_trace(y = data_fr$deaths, type = 'bar',name = 'New deaths') %>% 
        layout( barmode = 'stack')%>%layout(title ="Daily confirmend cases and deaths in France from 27/02/2020")
fig2
```
